\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-07-12 write_up/mixfishsim_ecolmod.tex
References added liberally

@@

Mortality $Z_{c,d}$ can be decomposed to natural mortality, $M_{c,d}$, and
fishing mortality, $F_{c,d}$, where both $M_{c,d}$ and $F_{c,d}$ are
instantaneous rates with $M_{c,d}$ fixed and $F_{c,d}$ calculated by solving
the Baranov catch equation \citep{Hilborn1992b} for $F_{c,d}$:
\begin{equation}
C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} * (1 - e^{-(F_{c,d} + M_{c,d})}) *
B_{c,d}
\end{equation}
where $C_{c,d}$ is the summed catch from the fishing model across all fleets
and vessels in cell $c$ for the population during the day $d$, and $B_{c,d}$
the daily biomass for the population in the cell. Here, catch and fishing
mortality are the sum of those across all fleets and vessels, where $F_{fl, v,
	c, d, p} = E_{fl, v, c, d} \cdot Q_{fl, p} \cdot B_{c, d, p}$ with
$fl$, $v$ and $p$ the fleet, vessel and population respectively and $E$ and $Q$
fishing effort and catchability. \todo{\added[id=CM]{[link $F$ to effort and
		catchability - as I think we have F as an emergent property of
		the fleets rather than something we solve for (I could be wrong
		though!) - catch for a vessel is a product of catchability and
		biomass, i.e. C = qB, but this catch is summed to solve for F.
		So its both really]}}\\

@@

Our results demonstrate the importance of considering data scale and resolution
when using observational data to support management measures. We find that
understanding of the community composition dynamics will depend on the level of
data aggregation and its important to consider the scale of processes;
including population movement rates, habitat uniformity and fishing targeting
practices if potential biases in data are to be understood and taken into
account. 
%% key findings in context
\subsection{How does data aggregation and source impact on spatial fisheries
	management measures?}

@@

We model the population and fleet dynamic processes in order to draw inference
on the importance of data scale and aggregation in understanding and managing
mixed fisheries and their impact on multiple fish populations. In doing so, we
have necessarily had to make a number of simplifying assumptions. \\

Fish populations in our simulations move in pre-defined timescales and
according to fixed habitat preferences and temperature gradients. Our
assumptions in parametrising the model (movement rates, temperature tolerances)
will have a direct impact on our conclusions on the relative importance of
spatial and temporal processes. These assumptions could be explored in a future
study by varying the parameters and assessing the robustness of our
conclusions. \\

In addition, we have assumed that fishing vessels are not restricted by quota
and therefore discarding of species for which vessels have no quota or that 
are unwanted is not taken into account. This is likely to be a significant
source of bias in any inference using commercial data and should also be
explored. \\

\subsection{Future application for framework}

@@

Other novel applications of our framework could be; testing different survey
designs given multiple species and data generating assumptions; commercial
index standardisation methods and approaches and understanding of appropriate
scales and data aggregations; exploring assumptions about the distribution of
natural mortality and fishing mortality throughout the year and importance of
capturing in-year dynamics in estimating stock status; at sea sampling scheme
designs to deliver unbiased estimates of population parameters; testing the
ability of commonly employed fleet dynamics models such as Random Utility
Models to capture finescale dynamics and understand their importance. \\

>>>>

Our framework allows users to explore the assumptions in modelling observational
data and evaluate the underlying dynamics of such approaches at a fine spatial
and temporal scale. \\

@@

Mortality $Z_{c,d}$ can be decomposed to natural mortality, $M_{c,d}$, and
fishing mortality, $F_{c,d}$, where both $M_{c,d}$ and $F_{c,d}$ are
instantaneous rates with $M_{c,d}$ fixed and $F_{c,d}$ calculated by solving
the Baranov catch equation \citep{Hilborn1992b} for $F_{c,d}$:
\begin{equation}
C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} * (1 - e^{-(F_{c,d} + M_{c,d})}) *
B_{c,d}
\end{equation}
where $C_{c,d}$ is the summed catch from the fishing model across all fleets
and vessels in cell $c$ for the population during the day $d$, and $B_{c,d}$
the daily biomass for the population in the cell. Here, catch and fishing
mortality are the sum of those across all fleets and vessels, where $F_{fl, v,
	c, d, p} = E_{fl, v, c, d} \cdot Q_{fl, p} \cdot D_{c, d, p}$ with
$fl$, $v$ and $p$ the fleet, vessel and population respectively and $E$ and $Q$
fishing effort and catchability of the gear, and $D$ is the density of the
population at the location fished. \todo{\added[id=CM]{[link $F$ to effort and
		catchability - as I think we have F as an emergent property of
		the fleets rather than something we solve for (I could be wrong
		though!) - catch for a vessel is a product of catchability and
		biomass, i.e. C = qB, but this catch is summed to solve for F.
		So its both really]}}\\

@@

Our results demonstrate the importance of considering data scale and resolution
when using observational data to support management measures. We find that
understanding of the community composition dynamics will depend on the level of
data aggregation and its important to consider the scale of processes;
including population movement rates, habitat uniformity and fishing targeting
practices if potential biases in data are to be understood and taken into
account.

EXPAND - relate to survey, commercial etc.. in Figure 2

%% key findings in context
\subsection{How does data aggregation and source impact on spatial fisheries
	management measures?}

@@

We model the population and fleet dynamic processes to draw inference on the
importance of data scale and aggregation in understanding and managing mixed
fisheries and their impact on multiple fish populations. In doing so, we have
necessarily had to make a number of simplifying assumptions. \\

Fish populations in our simulations move in pre-defined timescales and
according to fixed habitat preferences and temperature gradients (Figures
\ref{S-fig:1}, \ref{S-fig:3}). Our assumptions in parametrising the model
(movement rates, temperature tolerances) will have a direct impact on our
conclusions on the relative importance of spatial and temporal processes. These
assumptions could be explored in a future study by varying the parameters and
assessing the robustness of our conclusions. For our example application we
have chosen movement rates to reflect aggregation periods observed in past
studies \citep{Poos2007}. \\

In addition, we have assumed that fishing vessels are not restricted by quota
and therefore discarding of species for which vessels have no quota or that are
unwanted is not taken into account. This is likely to be a significant source
of bias in any inference using commercial data and should also be explored. For
example, MixFishSim could be altered to allow for spatiotemporal appraisal of
the impact of discarding on fisher behaviour and underlying populations via
inclusion as discarding behaviour, or through move-on rules or cessation of
fishing activity when quota is exhausted. \\

\subsection{Future applications of MixFishSim}

@@

Other novel applications of our framework could be; testing different survey
designs given multiple species and data generating assumptions \citep{Xu2015};
commercial index standardisation methods and approaches and understanding of
appropriate scales and data aggregations and non-proportionality in catch rate
and abundance \citep{Harley2001, Maunder2004}; exploring assumptions about the
distribution of natural mortality and fishing mortality throughout the year and
importance of capturing in-year dynamics in estimating stock status
\citep{Liu2013}; at sea sampling scheme designs to deliver unbiased estimates
of population parameters \cite{Cotter2007, Kimura2006}; adaptive management
\citep{Walters2007, Dunn2016}; testing the ability of commonly employed fleet
dynamics models such as Random Utility Models to capture fine scale dynamics
and understand their importance \cite{Girardin2016}; and as a detailed
operating model in a management strategy evaluation \cite{Mahevas2004}. \\
